Applications of the Fresnel Integrals

### 2019-03-17 draft.tex
spell check

	The generally accepted requirement for a proper transition curve is that the degree-of-curve
	shall increase gradually and uniformly from the point of tangent until the degree of the main
	curve is reached, and that the super-elevation9
	shall increase uniformly from zero at the
	tangent to the full amount at the connection with the main curve and yet have at any point
	the appropriate super-elevation for the curvature. In addition to this, an acceptable transition
	curve must be so simple that the field work may be easily and rapidly done, and should be so
	flexible that it may be adjusted to meet the varied requirements of problems in location and
	construction.
\end{quotation}

@@

\bibliographystyle{alphasorteprint}
\bibliography{bibliography.bib}
%\nocite{AS, BE, Sim, Str, WW}  % TODO: place in text
\end{document}

>>>>

	The generally accepted requirement for a proper transition curve is that the degree-of-curve
	shall increase gradually and uniformly from the point of tangent until the degree of the main
	curve is reached, and that the super-elevation shall increase uniformly from zero at the
	tangent to the full amount at the connection with the main curve and yet have at any point
	the appropriate super-elevation for the curvature. In addition to this, an acceptable transition
	curve must be so simple that the field work may be easily and rapidly done, and should be so
	flexible that it may be adjusted to meet the varied requirements of problems in location and
	construction.
\end{quotation}

@@

\bibliographystyle{alphasorteprint}
\bibliography{bibliography.bib}
\end{document}
